
\section{Curriculum Development Activities}\label{sec:curriculum}

%present a plan to integrate research outcomes into education and more broadly advance education in CPS;

PI Anderson teaches an intelligent robotics course to senior-level undergraduates and first-year graduate students.  This course will be augmented to include software engineering in robotics and embedded systems.  The prevailing architectures will be presented in terms of their use of standard distributed software engineering paradigms (transparency, cohesion, synchronous vs asynchronous processing, and real-time issues at both the operating system and the applications level), use of standard tool chains to enable reuse and code generation within RDIS and frameworks.  Students will learn to evaluate performance in terms of jitter, latency, and maintainability.  PI Syriani teaches an advance course for graduate students on model-based design (CS 691) and, in particular, domain-specific modeling techniques.  As part of the course project, some students are currently working on designing a domain-specific language for RDIS in both graphical and textual syntax. The results of this project will serve as a common case-study the student will be working on.  The PIs will continue to work with REU programs targeted at underrepresented groups (DREU, ARTSI, A4RC, etc) to incorporate summer research experiences for students on this project.  Undergraduate researchers will be incorporated to assist with coding, testing and documentation while learning important research skills such as reviewing relevant literature, writing and presenting research contributions.